Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-09-09 supplement.tex
supp figure edit

For the demographic modeling, we further subset to the regional populations,
from West Africa: Mende from Sierra Leone (MSL); South Africa: Nama from South
Africa (newly sequenced, Figure~\ref{fig:supp-nama}); East Africa: Gumuz
(traditionally hunter-gatherer with low levels of Eurasian admixture), Oromo
and Amhara (combined as traditionally agriculturalists with large proportion of
back-to-Africa Eurasian ancestry); and Europe: British (GBR). These were
combined with the high-coverage Vindija Neanderthal genome
\citep{Prufer2017-kk}, resulting in 290 total samples used in demographic
inference.

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/SuppFig_HDV.60_CEU.Nama}
    \caption{caption text}
    \label{fig:supp-nama}
\end{figure}

>>>>

For the demographic modeling, we further subset to the regional populations,
from West Africa: Mende from Sierra Leone (MSL); South Africa: Nama from South
Africa (newly sequenced); East Africa: Gumuz (traditionally hunter-gatherer
with low levels of Eurasian admixture), Oromo and Amhara (combined as
traditionally agriculturalists with large proportion of back-to-Africa Eurasian
ancestry); and Europe: British (GBR). These were combined with the
high-coverage Vindija Neanderthal genome \citep{Prufer2017-kk}, resulting in
290 total samples used in demographic inference.

@@
